---
title: "Practicing Worst Data Viz"
author: "Ruth Enriquez"
date: "2022-08-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(ggplot2)
library(paletteer)
library(sf)
library(janitor)
library(png)
library(patchwork)
library(dplyr)
library(grid)
```

```{r}
space_launch <- read_csv(here("data","space_launches.csv"))
```

```{r}
space_group <- space_launch |> 
  group_by(launch_year) |> 
  count(type) |> 
  rename(type_count = n)
```

```{r}
my_image <- readPNG(here("wut.png"))
```

```{r}
gg_space <- ggplot(data = space_group, aes(x = launch_year,
                                           y = type))+
  geom_point() +
    annotation_custom(rasterGrob(my_image,
                               width = unit(0.5,"npc"),
                               height = unit(0.7,"npc")),
                    -Inf, Inf, -Inf, Inf) +
  labs(title = "Minions Gain Control of S p a c e",
       subtitle = "WHAAAAAAAAAAAAAAT", 
       x= "R0Ck3t g0 B00M",
       y = "TO DA MOON")

gg_space
```

## **Task 2:**

Read in the SF emissions data set

```{r}
sf_inventory <- read_csv(here("data","San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))
```

Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

```{r}
sector_emissions <- sf_inventory %>%
  group_by(Sector_General, Calendar_Year) %>%
  summarize(total_greenhouse_mtCO2e = sum(Emissions_mtCO2e, na.rm = TRUE))
```

Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

```{r}
ycom_emissions <- sf_inventory |> 
  group_by(Calendar_Year, Commodity_Type)  |> 
  summarize(total_greenhouse_mtCO2e = sum(Emissions_mtCO2e, na.rm = TRUE))
```

Create a subset of the data that only contains observations from 2005 on, only for observations where `Sector_Detail2` contains the pattern "PG&E", then limit to columns `Calendar_Year`, `Sector_Detail2` and `Emissions_mtCO2e`

```{r}
sf_2005 <- sf_inventory |> 
  filter(Calendar_Year == 2005) |> 
  filter(str_detect(Sector_Detail2, pattern = "PG&E")) |> 
  select(Calendar_Year, Sector_Detail2, Emissions_mtCO2e)
```

## **Task 3: Do your data viz best**

Create a finalized graph (as perfect as you can make it) using the San Francisco GHG emissions dataset. **You** get to choose what you want to visualize. You can pick which variables & observations you're interested in. You may want to do some wrangling / summarizing first.


```{r}
sf_ghg <- sf_inventory |> 
  group_by(Sector_General) |> 
  select(Calendar_Year, Sector_General, Commodity_Type, Emissions_mtCO2e)
```

```{r}
sf_check <- sf_ghg |> 
  group_by(Sector_General) |> 
  filter(Sector_General %in% "Wastewater" | Sector_General %in% "Agriculture") |>
  select(Calendar_Year, Sector_General, Commodity_Type, Emissions_mtCO2e)
```


```{r}
sf_com <- sf_ghg |> 
  group_by(Commodity_Type) |> 
  summarize(total_greenhouse_mtCO2e = sum(Emissions_mtCO2e, na.rm = TRUE)) |> 
  select(Calendar_Year, Commodity_Type, Emissions_mtCO2e)
```





